\documentclass[11pt]{article}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{epstopdf}
\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `basename #1 .tif`.png}

\textwidth = 6.5 in
\textheight = 9 in
\oddsidemargin = 0.0 in
\evensidemargin = 0.0 in
\topmargin = 0.0 in
\headheight = 0.0 in
\headsep = 0.0 in
\parskip = 0.2in
\parindent = 0.0in

\newtheorem{theorem}{Theorem}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{definition}{Definition}

\title{Topics Available from HEP}
\author{Daniel D. Beatty}
\begin{document}
\maketitle

Astrophysics research at TTU

Careful on multiplex
\begin{itemize}\item random sample of a space 
\item random section
\item pre-bias to specified parameters
\begin{itemize}\item phase base space
\item develop means of running MC
\item Particle physics $\to$ applied math
\item 100s examples of improvement on accuracy and speed
\item Tools to note: BT, rootd\end{itemize}\end{itemize}


Astrophysics: SDSS
\begin{itemize}\item Detailed Numerical Analysis 
\item Common Astro Physics Tools and expansion
\begin{itemize}\item IRAF Image Reduction and Analysis Facility
\item DS9 \end{itemize}
\item Standard for image representation, FITS
\begin{itemize}\item File Format
\item Includes multiple methods of encoding
\item Analog to event container\end{itemize}\item Tools tend to be observatory specific and Linux oriented
\item SDSS needs a duplication of DR1
\item What are the opportunities with SDSS
\begin{itemize}\item Solve preview problem 
\item Emphasis features in the picture
\item Pull down menu options for analysis
\item Image Survey \end{itemize}\end{itemize}

Long-term: Super-Nova Accelerator Probe
\begin{itemize}\item Large CCD
\item Hardware problems
\item Examples
\begin{itemize}\item calibration
\item imaging \end{itemize}\end{itemize}

We come starting with SDSS leading up to SNAP with an interest in physics and computer science.  They have both hardware and software problems to deal with.  We can help by showing algorithmic, software, and development strength.   LBL, University of Michigan are our current competition and collaboration.  We can offer software for calibration.  

SDSS is a joint astronomy and computer science problem to produce the mathematical section of the problem.  A demonstration would be nice.  Definately work out the problem thoroughly.  

Keep up reading in Beylkin, Sweldon, Yellow Book.   Also build tools with Pantheon.  The key is tools for research and tools for contributions.  On the fly tools would be really nice.


Common mathematical tools: Matrix multiply, matrix inverse, and matrix PDE  Coefficient tree and matrices of energy distribution.  

Watch out for paperwork, committees, and the proposal.

 \end{document}