 Parallel and Grid Computing 
 
\begin{itemize}
\item Topics covered include
\begin{itemize}
\item History of Computing and Parallel Computing
\item Parallel Computing Paradigm
\item Shared versus Distributed memory architectures
\item Parallel Algorithm (mostly numerical algorithms)
\item Writing efficient code 
\item Grid computing and grid architectures
\item Distributed Memory System typically need the means of distributing the memory ``objects''.  
\item Class is not necessarily using a formal definition 
\end{itemize}
\item Course Requirements:
\begin{itemize}
\item Read and write simple C or Fortran codes 
\item Text: Parallel Programming with MPI by Peter S. Pacheco.
\item Grade will be determined by a project.
\begin{itemize}
\item The project must be approved in the first 5 weeks of the course.
\item It can be a programming project or a research paper.
\item You must report on the progress of this project every 3 weeks (by keeping an (e-) journal and turning it in.)
\end{itemize}

\end{itemize}
\item Industrial training class 
\begin{itemize}
\item You will learn by doing 
\item We will study code examples
\item We will modify these examples 
\item First Assignment  (obtain the account on hpcc)
\item Office hours are by appointment
\item Principle office in Admin 233 (hpcc) 
\item Second office in Math 241
\item Jerry Perez and Srirangam Addepalli are also available for assistance.  
\end{itemize}
\item Parallel Computing
\begin{itemize}
\item What is a parallel computing?
\item Why do we want to do it?
\item Many OS(s) appear to be parallel but they are not.  For example, multiuser OS(s) allow many users to log on simultaneously and carry out computations.
\item What is Grid computing?   (review Amdhal's Law and Moore's Law)

\begin{itemize}
\item What it is not: a single cluster of computers, one technology; or easy to implement
\item What it is:
\begin{itemize}
\item Compute Grid
\begin{itemize}
\item Secure, wide-area access to computing resources
\item Integrate existing clustering, queuing \& scheduling technology into seamless compute fab
\end{itemize}
\item Data Grid:
\begin{itemize}
\item Used for Enterprise Information Integration (EII). Simplifies the provisioning, access, and integrating of distributed data.
\end{itemize}

\end{itemize}


\end{itemize}


\end{itemize}
\item Does it affect you today?
\begin{itemize}
\item Automated Teller machines
\item Google (Web Server) 
\item Online transactions (airline tickets, catalogue buying i.e. LL Bean, etc.)
\item Routing of telephone calls
\end{itemize}
\item Military uses of computing (much of it parallel)
\begin{itemize}
\item Code breaking (NSA)
\item Weopon design 
\item Pointing and guiding weopons
\item Nuclear Stockpile assurance
\item Weather prediction
\end{itemize}
\item Commercial Use
\begin{itemize}
\item Modeling and Simulation
\item Desgining airplaines, cars pipelines, phonnes, ...
\item Human Genome project
\item Weather prediction
\item Data mining
\item Credit card fraud
\item Phone fraud
\item Marketing analyses
\item Database maintenance (ATM).
\end{itemize}
\item TTU HPC
\begin{itemize}\item Computational Number Theory
\item Fluid Flow 
\item Computational Chemistry 
\item Computational Physics
\item Multi-scale engineering computations
\item Stochastic ODE's and PDEs
\item Optimization
\item ??\end{itemize}
\item Immediate Future
\begin{itemize}\item Most supercomputing clusters are built from dual processor systems
\item This will be the first year (2005) that major semiconductor manufactures produces of dual core cpu
\item Quad core probably not far behind 
\item Will single core go away?\end{itemize}
\end{itemize}

submit MPI\_Job #np=4   
(rank of the processor)

HPCC is intending to use Putty and pscp on Windows platform.   
